Primary analysis

### 2022-09-16 analysis/primary.Rmd
add stats / change the fig size
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
```

@@

```{r seq-ioi, fig.width = 12, fig.height = 2.4}
ioi_seq <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Category, Articulation, Dynamics, Interval)]

@@

@@

```{r seq-kot, fig.width = 12, fig.height = 2.4}
kot_seq <- dt_kot[, .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, Category, Articulation, Dynamics, Interval)]

@@

@@

```{r seq-vel, fig.width = 12, fig.height = 2.4}
vel_seq <- dt_vel[, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Category, Articulation, Dynamics, RowNr)]

@@

@@

```{r seq-vel-diff, fig.width = 12, fig.height = 2.4}
vel_diff_seq <- dt_vel_diff[, .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Category, Articulation, Dynamics, Interval)]

@@

>>>>

# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# stats
if (!require("afex")) {install.packages("afex"); require("afex")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
```

@@

```{r seq-ioi, fig.width = 7, fig.height = 2}
ioi_seq <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Category, Articulation, Dynamics, Interval)]

@@

## 4. Stats

```{r}
aov_ez(
  data = ioi,
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation2", "Dynamics2")
)
```

@@

```{r seq-kot, fig.width = 7, fig.height = 2}
kot_seq <- dt_kot[, .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, Category, Articulation, Dynamics, Interval)]

@@

## 4. Stats

1) Legato

```{r}
aov_ez(
  data = kot[Articulation == "Legato"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation2", "Dynamics2")
)
```

2) Staccato

```{r}
aov_ez(
  data = kot[Articulation == "Staccato"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation2", "Dynamics2")
)
```

@@

```{r seq-vel, fig.width = 7, fig.height = 2}
vel_seq <- dt_vel[, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Category, Articulation, Dynamics, RowNr)]

@@

## 4. Stats

1) Forte

```{r}
aov_ez(
  data = vel[Dynamics == "Forte"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation2", "Dynamics2")
)
```

2) Piano

```{r}
aov_ez(
  data = vel[Dynamics == "Piano"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation2", "Dynamics2")
)
```

@@

```{r seq-vel-diff, fig.width = 7, fig.height = 2}
vel_diff_seq <- dt_vel_diff[, .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Category, Articulation, Dynamics, Interval)]

@@

## 4. Stats

1) FtoP

```{r}
aov_ez(
  data = vel_diff[Dynamics == "FtoP"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation2", "Dynamics2")
)
```

2) PtoF

```{r}
aov_ez(
  data = vel_diff[Dynamics == "PtoF"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation2", "Dynamics2")
)
```
